\documentclass[11pt,letter]{moderncv}

%\moderncvtheme[green]{casual}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage[hmargin=1cm,vmargin=0.5cm]{geometry}
%\usepackage[pdftex,colorlinks=false,plainpages=false]{hyperref}
\usepackage[pdftex,plainpages=false]{hyperref}

\firstname{Adam}
\familyname{DeConinck}
\email{ajdecon@ajdecon.org}
%\address{909 S 5th St \#139}{Champaign, IL 61820}
\mobile{347.709.2326}
\extrainfo{\href{http://www.ajdecon.org/}{http://www.ajdecon.org/}\\
		 \href{http://www.github.com/ajdecon}{http://www.github.com/ajdecon}}
\title{HPC Systems Engineer}

\nopagenumbers{}

\begin{document}
\maketitle

%\cvline{\large \textbf{Summary}}{\large Systems engineer focused on high-performance and scientific computing}


\section{Experience}
\cventry{2012--present}{Systems Engineer}{NVIDIA}{Santa Clara, CA}{}{
	\begin{itemize}
	\item Design, deploy, and support HPC clusters for development,
		benchmarking and demos.
	\item Primary system administrator for internal benchmarking cluster and Cray XK6 dev
		system.
	\item Develop automation for deploying compute clusters and demo systems to the cloud.
	\item Technical advice and support for marketing and solution architect teams
	\end{itemize}
}
\cventry{2011--present}{Contributer}{Warewulf Cluster Manager}{\href{http://warewulf.lbl.gov/}{http://warewulf.lbl.gov/}}{}{Development and testing for open-source HPC provisioning system and cluster manager. Have worked on IPMI integration, stateful
provisioning, and miscellaneous bugfixes.}
\cventry{2010--2012}{Systems Engineer}{R Systems NA, Inc.}{Champaign, IL}{}{Designed, deployed, and provided user support for Windows and Linux compute clusters as "HPC as a Service". Developed internal tooling and automation.}
\cventry{2007--2010}{Graduate Research Assistant}{University of Illinois}{Urbana, IL}{}{Research on viscoelastic materials and microfluidics, analysis of confocal microscopy data.}
\cventry{2006}{Contractor}{Dow Corning Corporation}{Midland, MI}{}{Assembled and programmed an automated test station to perform electrical characterization and optical analysis of prototype OLED devices}

\section{Skills and Knowledge}
\subsection{Programming Languages}
\cvdoubleitem{Python}{Simulations (NumPy), sysadmin}{Fortran}{Numerical simulations}
\cvdoubleitem{Perl}{Sysadmin, webapps, Warewulf}{C}{Some MPI programming}
\cvdoubleitem{Shell}{Sysadmin, misc scripting}{Java}{Image processing with ImageJ}
%\cvdoubleitem{Ruby}{Chef DSL, some scripting}{CUDA}{Help debug user code}
\subsection{High Performance Computing}
\cvline{Provisioning}{Warewulf, Windows HPC; some experience with Platform, Bright, Cobbler}
\cvline{Management}{Torque/Maui, PBS Professional, SLURM, Windows HPC Pack, Grid Engine, Hadoop}
\cvline{Storage}{Parallel filesystems including Lustre, HDFS, PVFS2; NFS for low-performance storage}
\cvline{Networking}{Deploy and manage Infiniband and Ethernet networks in clustered environments}
\cvline{Cloud}{Single-node and cluster deployments on Amazon EC2 and Peer 1}
\subsection{General System Administration}
\cvline{Support}{Front-line support for large, complex HPC deployments with up to 100 users}
%\cvline{Provisioning}{\small Linux: Perceus, Warewulf, Cobbler, Kickstart; Windows: HPC Pack, WDS}
\cvline{Configuration}{Configuration management with Chef or Ansible (Linux) or Group Policy (Windows)}
\cvline{Deployment}{Build packages (rpm/deb/msi) for custom application deployment}



\section{Education}
\cventry{2007--2010}{M.S. Materials Science and Engineering}{University of Illinois}{Urbana, IL}{}{}
\cventry{2003--2007}{B.S. Physics}{Michigan Technological University}{Houghton, MI}{}{Minors: Mathematics, Electronic Materials}

\section{Additional Training}
\cventry{2012}{Cray XE6/XK6 System Administration}{Cray, Inc.}{Chippewa Falls, WI}{}{}

\end{document}
